Performance of two different ontological and data access methods

### 2014-07-05 cold2014/magnus.tex
add references
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@731 43ef1190-90fd-4dd7-a769-d0121f02b80e
Removed some new lines
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@732 43ef1190-90fd-4dd7-a769-d0121f02b80e

Some pre-computations are done to make the application a little
more effective. This includes extracting all the model names from both
ontologies, initiate all possible partially defined products as a
PartialCar object and creating some internal structure. These
pre-computations were done so that it would be possible to present the
user with the name of each car model, not just the URI. We will also
describe more in depth how the car model search is done later on.

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{bibliography}

>>>>

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{bibliography,science}
